Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex

We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.

 and that there is a lot of room for improvement for our approach

 as well as in exploring other

>>>>

We have presented some ideas that are not completely explored but, based on the data we have available, seem to give comparable, or even better results than the other two approaches that tried to tackle the same problem. There is a lot of room for improvement of our approach, as well as in exploring other new ideas.

For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and use more systematic approach for choosing hyperparameters. It would be also interesting to try the trainable feature transformation approach on other authorship analysis problems.
